Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-31 draft.tex
differentiate between inside players' winning probabilities in prop 1 assumptions

\item \emph{For both players $g$ and $s$, $\frac {Q_{i0}}{1-\delta} \geq  -\zeta_i+\frac{W_{i0}(p_1) + L_{i0}(1-p_1)}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}

>>>>

\item \emph{For both players $g$ and $s$, $\frac {Q_{i0}}{1-\delta} \geq  -\zeta_i+\frac{W_{i0}(p_{1i}) + L_{i0}(1-p_{1i})}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}
